Calculating Biological Module Enrichment or Depletion and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}

### 2016-02-08 jss/article.tex
[Updated article]
- Updated figures
- updated default testing on all maps (but not master)
- updated enrichment results in article

\begin{verbatim}
> library(ACSNMineR)
> results <- enrichment(genes_test)
> dim(results)
[1] 36  9
> results[1,]
            module module_size nb_genes_in_module      genes_in_module
V12 Apoptosis:E2F1           5                  4 ATM E2F1 EP300 KAT2B
    universe_size nb_genes_in_universe      p.value p.value.corrected    test
V12          2133                   12 1.043478e-08       2.81739e-07 greater
\end{verbatim}

@@

  \begin{tabular}{l|c|c|c|c}
	\hline
Module & Mod. size & Genes in module & p-value & Test\\
	\hline
Apoptosis:E2F1 & 5 &  ATM E2F1 EP300 & 1.04e-08 & greater \\
               &   &  KAT2B                 &          &         \\
Apoptosis:G2 M CHECKPOINT & 35  & ATM KAT2B & 2.04e-02 & greater \\
Apoptosis:WNT CANONICAL & 53 & E2F1 EP300 KAT2B  & 4.98e-03 & greater \\
	\hline

@@

represent_enrichment(enrichment = list(Corrected = results[1:10,], 
Uncorrected = results_uncorrected[1:10,]),
                                plot = "heatmap", scale = "log", 
                                low = "steelblue" , high ="white", na.value = "grey")

@@

 represent_enrichment(enrichment = list(Corrected = results[1:10,], 
                             Uncorrected = results_uncorrected[1:10,]),
                               plot = "heatmap", scale = "reverselog", 
                               nrow = 1)
\end{verbatim}

>>>>

\begin{verbatim}
> library(ACSNMineR)
> results <- enrichment(genes_test)
> dim(results)
[1] 36  9
> results[1,]
             module module_size nb_genes_in_module    genes_in_module 
V17 APOPTOSIS_ENTRY          10                  4 ATM ATR CHEK2 E2F1          
    universe_size nb_genes_in_universe      p.value	p.value.corrected    test
V17      2241                   12 3.491372e-07	6.400849e-06 greater
\end{verbatim}

@@

  \begin{tabular}{l|c|c|c|c}
	\hline
Module & Mod. size & Genes in module & p-value & Test\\
	\hline
CellCycle & 242 & ATM ATR CHEK2   & 5.36e-07 & greater \\
          &   &  CREBBP KAT2B TFDP1   &          &         \\
          &   &  E2F1 EP300 HDAC1    &          &         \\
          &	  & GTF2H1 GTF2H2 GTF2H2B &	& \\
CellCycle: APOPTOSIS ENTRY & 10 & ATM ATR CHEK2 E2F1 & 3.49e-07 & greater \\
CellCycle: CYCLINB			& 7  & ATM 				  & 3.98e-02 & greater \\

	\hline

@@

represent_enrichment(enrichment = list(Corrected = results[1:6,], 
Uncorrected = results_uncorrected[1:6,]),
                                plot = "heatmap", scale = "reverselog", 
                                low = "steelblue" , high ="white", na.value = "grey")

@@

 represent_enrichment(enrichment = list(Corrected = results[1:6,], 
                             Uncorrected = results_uncorrected[1:6,]),
                               plot = "heatmap", scale = "reverselog", 
                               nrow = 1)
\end{verbatim}
